Appendix: A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-10 appendix.Rmd
checking table C1

>>>>

Throughout the study, we have collected `r vi_survey %>% filter(!attention_check, !null_lineup) %>% nrow()` evaluations on `r vi_survey %>% filter(!attention_check, !null_lineup) %>% count(unique_lineup_id) %>% nrow()` non-null lineups. Table \ref{tab:count-lineup} gives further details about the number of evaluations, lineups and participants over pattern types and data collection periods.

```{r}
# Calculate these numbers
matrix(c(c(576, 0, 144, 0, 540, 135, 1116),
         c(2880, 0, 864, 0, 2700, 810, 7254),
         c(160, 0, 123, 0, 160, 123, 443)),
       ncol = 7,
       byrow = TRUE) %>%
  data.frame() %>%
  add_column(name = c("Lineups", "Evaluations", "Participants"), .before = 1) %>%
  kableExtra::kable(format = "latex", 
                    booktabs = TRUE,
                    label = "count-lineup",
                    caption = "Count of lineups, evaluations and participants over departure types and data collection periods.",
                    col.names = c("Number", "I", "II", "III", "I", "II", "II", "Total")) %>%
  kableExtra::add_header_above(c(" " = 1, "Non-linearity" = 3, "Heteroskedasticity" = 3))
```

### 2023-04-10 appendix.tex
checking table C1

Throughout the study, we have collected 7254 evaluations on 1116
non-null lineups. Table \ref{tab:count-lineup} gives further details
about the number of evaluations, lineups and participants over departure
types and data collection periods.

>>>>

Throughout the study, we have collected 7254 evaluations on 1116
non-null lineups. Table \ref{tab:count-lineup} gives further details
about the number of evaluations, lineups and participants over pattern
types and data collection periods.
